---
title: "Metro - Case Study"
author: "Cristhian Jimenez"
date: "8/24/2018"
output: ioslides_presentation
incremental: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rpivotTable)
library(tibble)
library(chron)
library(lubridate)
library(zoo)
library(dplyr)
library(reshape)
library(reshape2)
library(plotly)
library(stringr)
library(forecast)
library(xts)
library(numbers)
library(shiny)
library(knitr)
library(kableExtra)

TSAnalysis <- function(ts, lags=20){
  ts <- na.omit(ts)
  par(mfrow=c(2,1))
  #win.graph(width=4.875,height=3,pointsize=8)
  #forecast::Acf(ts,lags, ci.type='ma', xlab = "", main="")
  acf(ts,lags, ci.type='ma', xlab = "", main="")
  #win.graph(width=4.875,height=3,pointsize=8)
  forecast::Pacf(ts,lags, main = "")
  par(mfrow=c(1,1))
}
plotgg <- function(ser1, ser2){
  n1 = names(ser1)
  print(n1)
  n2 = names(ser1)
  plotfun <- as.data.frame(
    cbind(ts = seq(1, length(ser1), by =1 ),
          orig = ser1,
          fore = ser2))
  plotfun <- reshape2::melt(plotfun, id="ts")
  p <- ggplot2::ggplot(data = plotfun,
              aes(x = ts, 
                  y = value, 
                  colour = variable )) +
    geom_line()+
    xlab('Time')+
    ylab('Value')+
    theme_minimal()
  
  plotly::ggplotly(p)
}
setwd('C:/Users/a688291/Downloads/Personal/')
path = 'C:/Users/a688291/Downloads/Personal/'

data_metro <- read.csv(file= paste(path,"data.csv", sep = ""),
                         header = TRUE, 
                         sep=",")


data_metro$calendar_date <- lubridate::mdy(data_metro$calendar_date)
```

## Contents

- EDA 
- Variables
- Model
- Results
- Conclusion


## EDA 
output variable: volume_sold.
```{r, include=FALSE}
data_metro <- as.tbl(data_metro)

data_metro_eda <- data_metro %>%
  select(calendar_date, 
         product_id,
         volume_sold,
         revenue,
         cost,
         stock_level,
         retail_price,
         mpdm1,
         vwm1,
         woy) %>%
  arrange(product_id,as.Date(calendar_date))

p1 <- ggplot(data = data_metro_eda)+
  geom_line(aes(x = as.Date(calendar_date), y=volume_sold, colour = as.character(product_id)))+
  labs(colour = "Product id")+
  xlab("Date")+
  ylab("Number of units")+
  theme_minimal()

```



```{r}
ggplotly(p1) 

```

## EDA 

```{r, include=FALSE}
p1 <- ggplot(data = data_metro_eda)+
  geom_boxplot(aes(x=as.character(product_id), y=volume_sold))+
  labs(colour = "Product id")+
  xlab("Product id")+
  ylab("Number of units")+
  theme_minimal()
```
```{r}
ggplotly(p1)

```
```{r, include=FALSE}

mpdi <- mean(
  filter(data_metro_eda, product_id == 158105)$volume_sold
)
 
data_metro_eda <- data_metro_eda %>%
  mutate(
    volume_sold = dplyr::if_else(product_id == 158105 & volume_sold == 4909,
                                       mpdi,
                                       as.double(volume_sold)
                                       )
    ) %>%
  mutate(volume_sold= dplyr::if_else(volume_sold<0,0,as.double(volume_sold))
         )

p1 <- ggplot(data = data_metro_eda)+
  geom_boxplot(aes(x=as.character(product_id), y=as.double(volume_sold), colour= as.character(product_id)))+
  labs(colour = "Product id")+
  xlab("Product id")+
  ylab("Number of units")+
  theme_minimal()

```

## EDA
After modifications of variable volume_sold.

```{r}

pseries <- ggplot(data = data_metro_eda)+
  geom_line(aes(x = as.Date(calendar_date), y=volume_sold, colour = as.character(product_id)))+
  labs(colour = "Product id")+
  xlab("Date")+
  ylab("Number of units")+
  theme_minimal()

cowplot::plot_grid(p1, pseries, nrow=2)

#modified volume_sold variable, no peaks and no values under 0
```


##EDA

```{r, include=FALSE}
totalVolumeSold <- sum(data_metro_eda$volume_sold)
data_metro_tbl <- data_metro_eda %>%
  ungroup() %>%
  group_by(product_id) %>%
  summarise(pct_volume = round(100 * sum(volume_sold)/totalVolumeSold, 2),
            pct_zeroes = round(100*sum(volume_sold==0)/sum(volume_sold!=0),2)
            )
  
```
Let's consider that one product makes more than 70% of the total amount of volume, as well as the different shape of its time series.

```{r}

knitr::kable(data_metro_tbl,format = "html" ,padding = 0)%>%
  kable_styling(position="center", full_width = FALSE, bootstrap_options = "striped")
```

##Variables

- volume_sold: outcome variable
- revenue: depends on volume sold
- cost: depends on volume sold
- stock_level: consider in the model
- retail_price: consider in the model
- mpdm1: consider in the model


The model was built considering the direct effects on sales (volume sold) of a set of variables.

##Variables
```{r, include=FALSE}

data_metro_pid <- data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(stock_levelLag  = dplyr::lag(stock_level, default = mean(stock_level)),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price))) %>%
  select(calendar_date, volume_sold, stock_levelLag)

data_metro_pid <- reshape2::melt(as.data.frame(data_metro_pid), id = "calendar_date")

p1 <- ggplot(data = data_metro_pid)+
  geom_line(aes(x = as.Date(calendar_date), y=value, colour = variable))+
  labs(colour = "Variable")+
  xlab("Date")+
  ylab("Units")+
  theme_minimal()

data_metro_pid <- data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(stock_levelLag  = dplyr::lag(stock_level, default = mean(stock_level)),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price))) %>%
  select(calendar_date,retail_priceLag, mpdm1)

data_metro_pid <- reshape2::melt(as.data.frame(data_metro_pid), id = "calendar_date")

p2 <- ggplot(data = data_metro_pid)+
  geom_line(aes(x = as.Date(calendar_date), y=value, colour = variable))+
  labs(colour = "Variable")+
  xlab("Date")+
  ylab("Units")+
  theme_minimal()

```
```{r}

data_metro_pid <- data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))%>%
  select(calendar_date, priceLag)

p3 <- ggplot(data = data_metro_pid)+
  geom_line(aes(x = as.Date(calendar_date), y=priceLag), group = 1 , colour="tomato1")+
  xlab("Date")+
  ylab("Units")+
  theme_minimal()


cowplot::plot_grid((p1), (p2), p3, nrow = 3)


```

##Model 
-Weekly aggregation with lags for stock and price variables. Product id 13701.

```{r}
data_metro_pid <-  data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))

data_metro_pid <- data_metro_pid %>%
  group_by(woy) %>%
  summarise(volume_sold = sum(volume_sold),
            priceLag = sum(priceLag)/n(),
            stock_levelLag = sum(stock_levelLag)
            )%>%
  filter(woy<48)

p<- ggplot(data_metro_pid)+
  geom_line(aes(x=woy,y=volume_sold, colour="VolumeSold"), group=1)+
  geom_line(aes(x=woy,y=stock_levelLag, colour="StockLevelLag"), group=1)+
  geom_line(aes(x=woy,y=124*priceLag-1352, colour="priceLag"), group=1)+
  scale_colour_manual("", 
                      breaks = c("VolumeSold", "StockLevelLag", "priceLag"),
                      values = c("tomato1", "royalblue1", "orange2")) +
  xlab("week of year")+
  ylab("units")+
  theme_minimal()
ggplotly(p)

```

##Model 
-Weekly aggregation with lags for stock and price variables. Product id 26104 and 158105.

```{r}
data_metro_pid <-  data_metro_eda %>%
  ungroup() %>%
  filter(product_id %in% c(26104,158105)) %>%
  group_by(calendar_date) %>%
  summarise(retail_price = mean(retail_price),
            mpdm1 = mean(mpdm1),
            stock_level = sum(stock_level),
            volume_sold = sum(volume_sold),
            woy = max(woy)
            )
  

data_metro_pid <-  data_metro_pid %>%
  ungroup() %>%
  #filter(product_id==26104 || product_id==158105) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))

data_metro_pid <- data_metro_pid %>%
  group_by(woy) %>%
  summarise(volume_sold = sum(volume_sold),
            priceLag = sum(priceLag)/n(),
            stock_levelLag = sum(stock_levelLag)
            )%>%
  filter(woy<48)

p<- ggplot(data_metro_pid)+
  geom_line(aes(x=woy,y=(volume_sold), colour="VolumeSold"), group=1)+
  geom_line(aes(x=woy,y=0.05*(stock_levelLag), colour="StockLevelLag"), group=1)+
  geom_line(aes(x=woy,y=20*(priceLag), colour="priceLag"), group=1)+
  scale_colour_manual("", 
                      breaks = c("VolumeSold", "StockLevelLag", "priceLag"),
                      values = c("tomato1", "royalblue1", "orange2")) +
  xlab("week of year")+
  ylab("units")+
  theme_minimal()
ggplotly(p)

```


##Model 
-Weekly aggregation with lags for stock and price variables. Product id 158737.

```{r}
data_metro_pid <-  data_metro_eda %>%
  ungroup() %>%
  filter(product_id==158737) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))

data_metro_pid <- data_metro_pid %>%
  group_by(woy) %>%
  summarise(volume_sold = sum(volume_sold),
            priceLag = sum(priceLag)/n(),
            stock_levelLag = sum(stock_levelLag)
            )%>%
  filter(woy<48)

p<- ggplot(data_metro_pid)+
  geom_line(aes(x=woy,y=volume_sold, colour="VolumeSold"), group=1)+
  geom_line(aes(x=woy,y=0.2*stock_levelLag, colour="StockLevelLag"), group=1)+
  geom_line(aes(x=woy,y=24*priceLag-1352, colour="priceLag"), group=1)+
  scale_colour_manual("", 
                      breaks = c("VolumeSold", "StockLevelLag", "priceLag"),
                      values = c("tomato1", "royalblue1", "orange2")) +
  xlab("week of year")+
  ylab("units")+
  theme_minimal()
ggplotly(p)

```

##Model
Linear regression with ARIMA errors for product id 13701.

```{r}
data_metro_pid <-  data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))

data_metro_pid <- data_metro_pid %>%
  group_by(woy) %>%
  summarise(volume_sold = sum(volume_sold),
            priceLag = sum(priceLag)/n(),
            stock_levelLag = sum(stock_levelLag),
            vwm1 = mean(vwm1)
            )%>%
  filter(woy<48)

ser.model      <- data_metro_pid$volume_sold
ser.price      <- data_metro_pid$priceLag
ser.stock      <- data_metro_pid$stock_levelLag
ser.vwm1       <- data_metro_pid$vwm1


exo.vars <- data.frame(
  cbind(price    = log(ifelse(ser.price<0, 0, ser.price)+1),
        stock    = log(ifelse(ser.stock<0, 0, ser.stock)+1),
        vwm1     = log(ser.vwm1+1)
  )
)

model.exo13701 <- forecast::Arima(
  log(ser.model+1),
  order = c(6,0,0),
  xreg = exo.vars,
  include.drift = FALSE)

ser.for.13701 <- forecast::forecast(model.exo13701, xreg = exo.vars[43:47,])

##########################################################################################
##########################################################################################


data_metro_pid <-  data_metro_eda %>%
  ungroup() %>%
  filter(product_id %in% c(26104,158105)) %>%
  group_by(calendar_date) %>%
  summarise(retail_price = mean(retail_price),
            mpdm1 = mean(mpdm1),
            stock_level = sum(stock_level),
            volume_sold = sum(volume_sold),
            vwm1 = mean(vwm1),
            woy = max(woy)
            )

data_metro_pid <-  data_metro_pid %>%
  ungroup() %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))

data_metro_pid <- data_metro_pid %>%
  group_by(woy) %>%
  summarise(volume_sold = sum(volume_sold),
            priceLag = sum(priceLag)/n(),
            stock_levelLag = sum(stock_levelLag),
            vwm1 = mean(vwm1)
            )%>%
  filter(woy<48)


ser.model      <- data_metro_pid$volume_sold
ser.price      <- data_metro_pid$priceLag
ser.stock      <- data_metro_pid$stock_levelLag
ser.vwm1       <- data_metro_pid$vwm1


exo.vars <- data.frame(
  cbind(price    = log(ifelse(ser.price<0, 0, ser.price)+1),
        stock    = log(ifelse(ser.stock<0, 0, ser.stock)+1),
        vwm1     = log(ser.vwm1+1)
        #ratio    = log(ser.ratio+1),
        # ser.outliers ,
        # ser.outliers1
  )
)
 
# method = c("CSS-ML", "ML", "CSS")

#TSAnalysis(ser.model, 50)


model.exo26104 <- forecast::auto.arima(
  log(ser.model+1),
  
  xreg = exo.vars)

model.exo26104 <- forecast::Arima(
  log(ser.model+1),
  order = c(1,0,0),
  xreg = exo.vars,
  include.drift = FALSE)

ser.for.26104 <- forecast::forecast(model.exo26104, xreg = exo.vars[43:47,])
##########################################################################################
##########################################################################################


data_metro_pid <-  data_metro_eda %>%
  ungroup() %>%
  filter(product_id==158105) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))

data_metro_pid <- data_metro_pid %>%
  group_by(woy) %>%
  summarise(volume_sold = sum(volume_sold),
            priceLag = sum(priceLag)/n(),
            stock_levelLag = sum(stock_levelLag),
            vwm1 = mean(vwm1)
            )%>%
  filter(woy<48)

# p<- ggplot(data_metro_pid)+
#   geom_line(aes(x=woy,y=volume_sold, colour="VolumeSold"), group=1)+
#   geom_line(aes(x=woy,y=stock_levelLag, colour="StockLevelLag"), group=1)+
#   geom_line(aes(x=woy,y=124*priceLag-1352, colour="priceLag"), group=1)+
#   scale_colour_manual("", 
#                       breaks = c("VolumeSold", "StockLevelLag", "priceLag"),
#                       values = c("tomato1", "royalblue1", "orange2")) +
#   xlab("week of year")+
#   ylab("units")+
#   theme_minimal()
# ggplotly(p)

ser.model      <- data_metro_pid$volume_sold
ser.price      <- data_metro_pid$priceLag
ser.stock      <- data_metro_pid$stock_levelLag
ser.vwm1       <- data_metro_pid$vwm1


exo.vars <- data.frame(
  cbind(price    = log(ifelse(ser.price<0, 0, ser.price)+1),
        stock    = log(ifelse(ser.stock<0, 0, ser.stock)+1),
        vwm1     = log(ser.vwm1+1)
  )
)

model.exo158105 <- forecast::Arima(
  log(ser.model+1),
  order = c(1,0,0),
  xreg = exo.vars,
  include.drift = FALSE)
  
ser.for.158105 <- forecast::forecast(model.exo158105, xreg = exo.vars[43:47,])
##########################################################################################
##########################################################################################


data_metro_pid <-  data_metro_eda %>%
  ungroup() %>%
  filter(product_id==158737) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))

data_metro_pid <- data_metro_pid %>%
  filter(woy<48) %>%
  group_by(woy) %>%
  summarise(volume_sold = sum(volume_sold),
            priceLag = sum(priceLag)/n(),
            stock_levelLag = sum(stock_levelLag),
            vwm1 = mean(vwm1)
            )
  

ser.model      <- data_metro_pid$volume_sold
ser.price      <- data_metro_pid$priceLag
ser.stock      <- data_metro_pid$stock_levelLag
ser.vwm1       <- data_metro_pid$vwm1
ser.outlier    <-  1*(seq(data_metro_pid$volume_sold)==36)


exo.vars <- data.frame(
  cbind(price    = log(ifelse(ser.price<0, 0, ser.price)+1),
        stock    = log(ifelse(ser.stock<0, 0, ser.stock)+1),
        vwm1     = log(ser.vwm1+1)
        #outlier  = ser.outlier
  )
)


model.exo158737 <- forecast::auto.arima(
  log(ser.model+1),
  xreg = exo.vars)

model.exo158737 <- forecast::Arima(
  log(ser.model+1),
  order = c(1,0,0),
  xreg = exo.vars,
  include.drift = FALSE)

ser.for.158737 <- forecast::forecast(model.exo158737, xreg = exo.vars[43:47,])
#ser.for.158737 <- forecast::forecast(model.exo158737, xreg = exo.vars[320:329,])

(model.exo13701)



```
##Model
Linear regression with ARIMA errors for product id 26104 and 158105.
```{r}
(model.exo26104)
# (model.exo158105)
# (model.exo158737)
```


##Model
Linear regression with ARIMA errors for product id 158737.
```{r}
# (model.exo26104)
# (model.exo158105)
(model.exo158737)
```


##Results

Fit and residuals for product id 13701.
```{r}
ori = exp(as.double(ser.for.13701$x))-1
fore = exp(as.double(ser.for.13701$fitted))-1
res = ori-fore

plotfun <- as.data.frame(
    cbind(ts = seq(1, length(ori), by =1 ),
          orig = ori,
          fore = fore,
          res = res))
p<-ggplot(plotfun)+
  geom_line(aes(x=ts,y=orig, colour="Original" ), group =1)+
  geom_line(aes(x=ts,y=fore, colour="Forecast" ), group =1)+
  geom_bar(aes(x=ts,y = res, colour="Residuals"), stat="identity", group=1)+
  scale_colour_manual("", 
                      breaks = c("Original", "Forecast", "Residuals"),
                      values = c("tomato1", "royalblue2", "gray80"))+
  xlab("Week")+
  ylab("Volume sold")+
  theme_minimal()

acc.13701 <- accuracy(ori,fore)

plotly::ggplotly(p)

```

##Results
Fit and residuals for product id 26104 and 158105.
```{r}
ori = exp(as.double(ser.for.26104$x))-1
fore = exp(as.double(ser.for.26104$fitted))-1
res = ori-fore

plotfun <- as.data.frame(
    cbind(ts = seq(1, length(ori), by =1 ),
          orig = ori,
          fore = fore,
          res = res))
p<-ggplot(plotfun)+
  geom_line(aes(x=ts,y=orig, colour="Original" ), group =1)+
  geom_line(aes(x=ts,y=fore, colour="Forecast" ), group =1)+
  geom_bar(aes(x=ts,y = res, colour="Residuals"), stat="identity", group=1)+
  scale_colour_manual("", 
                      breaks = c("Original", "Forecast", "Residuals"),
                      values = c("tomato1", "royalblue2", "gray80"))+
  xlab("Week")+
  ylab("Volume sold")+
  theme_minimal()

acc.26104 <- accuracy(ori,fore)

plotly::ggplotly(p)

```


##Results
Fit and residuals for product id 158737.
```{r}
ori = exp(as.double(ser.for.158737$x))-1
fore = exp(as.double(ser.for.158737$fitted))-1
res = ori-fore

plotfun <- as.data.frame(
    cbind(ts = seq(1, length(ori), by =1 ),
          orig = ori,
          fore = fore,
          res = res))
p<-ggplot(plotfun)+
  geom_line(aes(x=ts,y=orig, colour="Original" ), group =1)+
  geom_line(aes(x=ts,y=fore, colour="Forecast" ), group =1)+
  geom_bar(aes(x=ts,y = res, colour="Residuals"), stat="identity", group=1)+
  scale_colour_manual("", 
                      breaks = c("Original", "Forecast", "Residuals"),
                      values = c("tomato1", "royalblue2", "gray80"))+
  xlab("Week")+
  ylab("Volume sold")+
  theme_minimal()

acc.158737 <- accuracy(ori,fore)

plotly::ggplotly(p)
```

##Results

```{r}
acc.13701  <- c("13701" , round(acc.13701[5],2) )
acc.26104  <- c("26104" , round(acc.26104[5],2) )
acc.158737 <- c("158737", round(acc.158737[5],2) )

cfd <- data.frame(rbind(acc.13701, acc.26104, acc.158737))
colnames(cfd) <- c("Product id", "MAPE")

cfd <- as.tbl(cfd) 

knitr::kable(cfd, format = "html" ,padding = 0)%>%
  kable_styling(position="center", full_width = FALSE, bootstrap_options = "striped")

```





