---
title: "Metro - Case Study"
author: "Cristhian Jim??nez"
date: "8/24/2018"
output: ioslides_presentation
incremental: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rpivotTable)
library(tibble)
library(chron)
library(lubridate)
library(zoo)
library(dplyr)
library(reshape)
library(reshape2)
library(plotly)
library(stringr)
library(forecast)
library(xts)
library(numbers)
library(shiny)
library(knitr)
library(kableExtra)

TSAnalysis <- function(ts, lags=20){
  ts <- na.omit(ts)
  par(mfrow=c(2,1))
  #win.graph(width=4.875,height=3,pointsize=8)
  #forecast::Acf(ts,lags, ci.type='ma', xlab = "", main="")
  acf(ts,lags, ci.type='ma', xlab = "", main="")
  #win.graph(width=4.875,height=3,pointsize=8)
  forecast::Pacf(ts,lags, main = "")
  par(mfrow=c(1,1))
}

setwd('/Users/Cristhian/Documents/Metro/case_study/')
path = '/Users/Cristhian/Documents/Metro/case_study/'

data_metro <- read.csv(file= paste(path,"data.csv", sep = ""),
                         header = TRUE, 
                         sep=",")

distinct(data_metro,calendar_date)
data_metro$calendar_date <- lubridate::mdy(data_metro$calendar_date)
```

## Contents

- EDA 
- Variables
- Model
- Results
- Conclusion


## EDA 
output variable: volume_sold
```{r, include=FALSE}
data_metro <- as.tbl(data_metro)

data_metro_eda <- data_metro %>%
  group_by(calendar_date, product_id) %>%
  summarise(volume_sold = sum(volume_sold),
            revenue = sum(revenue),
            cost = sum(cost),
            stock_level = sum(stock_level),
            retail_price = sum(retail_price),
            mpdm1 = sum(mpdm1)) %>%
  arrange(product_id,as.Date(calendar_date))

p1 <- ggplot(data = data_metro_eda)+
  geom_line(aes(x = as.Date(calendar_date), y=volume_sold, colour = as.character(product_id)))+
  labs(colour = "Product id")+
  xlab("Date")+
  ylab("Number of units")+
  theme_minimal()

```



```{r}
ggplotly(p1) 

```

## EDA 

```{r, include=FALSE}
p1 <- ggplot(data = data_metro_eda)+
  geom_boxplot(aes(x=as.character(product_id), y=volume_sold))+
  labs(colour = "Product id")+
  xlab("Product id")+
  ylab("Number of units")+
  theme_minimal()
```
```{r}
ggplotly(p1)

```
```{r, include=FALSE}

mpdi <- mean(
  filter(data_metro_eda, product_id == 158105)$volume_sold
)
 
data_metro_eda <- data_metro_eda %>%
  mutate(
    volume_sold = dplyr::if_else(product_id == 158105 & volume_sold == 4909,
                                       mpdi,
                                       as.double(volume_sold)
                                       )
    ) %>%
  mutate(volume_sold= dplyr::if_else(volume_sold<0,0,as.double(volume_sold))
         )

p1 <- ggplot(data = data_metro_eda)+
  geom_boxplot(aes(x=as.character(product_id), y=volume_sold))+
  labs(colour = "Product id")+
  xlab("Product id")+
  ylab("Number of units")+
  theme_minimal()

```

## EDA
After modifications of variable volume_sold

```{r}

pseries <- ggplot(data = data_metro_eda)+
  geom_line(aes(x = as.Date(calendar_date), y=volume_sold, colour = as.character(product_id)))+
  labs(colour = "Product id")+
  xlab("Date")+
  ylab("Number of units")+
  theme_minimal()

cowplot::plot_grid(p1, pseries, nrow=2)

#modified volume_sold variable, no peaks and no values under 0
```


##EDA

```{r, include=FALSE}
totalVolumeSold <- sum(data_metro_eda$volume_sold)
data_metro_tbl <- data_metro_eda %>%
  ungroup() %>%
  group_by(product_id) %>%
  summarise(pct_volume = round(100 * sum(volume_sold)/totalVolumeSold, 2) )
  
```
Let's consider that one product makes more than 70% of the total amount of volume, as well as the different shape of its time series.

```{r}

knitr::kable(data_metro_tbl,format = "html" ,padding = 0)%>%
  kable_styling(position="center", full_width = FALSE, bootstrap_options = "striped")
```

##Variables

- volume_sold: outcome variable
- revenue: depends on volume sold
- cost: depends on volume sold
- stock_level: consider in the model
- retail_price: consider in the model
- mpdm1: consider in the model


The model was built considering the direct effects on sales (volume sold) of a set of variables.

##Variables
```{r, include=FALSE}

data_metro_pid <- data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(stock_levelLag  = dplyr::lag(stock_level, default = mean(stock_level)),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price))) %>%
  select(calendar_date, volume_sold, stock_levelLag)

data_metro_pid <- reshape2::melt(data_metro_pid, id = "calendar_date")

p1 <- ggplot(data = data_metro_pid)+
  geom_line(aes(x = as.Date(calendar_date), y=value, colour = variable))+
  labs(colour = "Variable")+
  xlab("Date")+
  ylab("Units")+
  theme_minimal()

data_metro_pid <- data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(stock_levelLag  = dplyr::lag(stock_level, default = mean(stock_level)),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price))) %>%
  select(calendar_date,retail_priceLag, mpdm1)

data_metro_pid <- reshape2::melt(data_metro_pid, id = "calendar_date")

p2 <- ggplot(data = data_metro_pid)+
  geom_line(aes(x = as.Date(calendar_date), y=value, colour = variable))+
  labs(colour = "Variable")+
  xlab("Date")+
  ylab("Units")+
  theme_minimal()

```
```{r}

data_metro_pid <- data_metro_eda %>%
  ungroup() %>%
  filter(product_id==13701) %>%
  mutate(retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         mpdm1D = lag(mpdm1),
         mpdm1FixedLag = dplyr::if_else(mpdm1 == 0 , mpdm1D, mpdm1 ),
         retail_priceLag = dplyr::lag(retail_price, default = mean(retail_price)),
         stock_levelLag = dplyr::lag(stock_level, default = mean(stock_level)),
         priceLag = dplyr::if_else(mpdm1FixedLag<retail_priceLag,retail_priceLag,mpdm1FixedLag))%>%
  select(calendar_date, priceLag)
p3 <- ggplot(data = data_metro_pid)+
  geom_line(aes(x = as.Date(calendar_date), y=priceLag), group = 1)+
  xlab("Date")+
  ylab("Units")+
  theme_minimal()


cowplot::plot_grid((p1), (p2), p3, nrow = 3)


```


